Refactoring the Candidate Cancer Gene Database

### 2021-05-21 presentation.Rmd
final

- Tim Starr*
- Yuk Sham*
- Jinhua Wang
- National Marrow Donor Program
- UMN-OIT
- Cassandra Price
- My wife and parents

>>>>

- Tim Starr*
- Yuk Sham*
- Jinhua Wang
- Ken Abbott
- BICB program
- National Marrow Donor Program
- UMN-OIT
- Judy Cho
- Phil Schumm
- Cassandra Price
- Nouf Gazdar
- My wife and parents
